%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A general CV with all my experiences
%
% Based on the template of Leo Uieda's CV
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}

% Identifying information
\newcommand{\Title}{Community Researcher and Programme Coordinator}
\newcommand{\FirstName}{Ana Caroline}
\newcommand{\LastName}{Colombo}
\newcommand{\Initials}{AC}
\newcommand{\MyName}{\FirstName\ \LastName}
\newcommand{\Me}{\textbf{\LastName, \Initials}}  % For citations
\newcommand{\Email}{acarolcolombo@gmail.com}
\newcommand{\Website}{acarolcolombo.com}
\newcommand{\ORCID}{0000-0002-6547-0340}
\newcommand{\phone}{+44 0757 718 7908}
%\newcommand{\Affiliation}{}
\newcommand{\Address}{19 Bowden Road}
\newcommand{\City}{L19 1QN - Liverpool, UK}

% Names for citing coauthors
\newcommand{\Amanda}{De Oliveira, AR}
\newcommand{\Adriano}{Reimer, AE}
\newcommand{\Brandao}{Brandão, ML}
\newcommand{\Muthu}{Muthuraju, S}
\newcommand{\Rafael}{Almada, RC}
\newcommand{\Marcio}{Rodrigues, ML}
\newcommand{\Viviane}{Saito, VM}
\newcommand{\Teddy}{Talbot, T}
\newcommand{\Pag}{Rizzo, J}
\newcommand{\Zamith}{Zamith-Miranda, D}
\newcommand{\Va}{Silva, VKA}
\newcommand{\Jeremy}{Allegood, JC}
\newcommand{\Casadevall}{Casadevall, A}
\newcommand{\Maurizio}{Del Poeta, M}
\newcommand{\Josh}{Nosanchuk, JD}
\newcommand{\Kronstad}{Kronstad, JW}
\newcommand{\Nayara}{Barroca, NCB}
\newcommand{\Mariana}{Guarda, MD}
\newcommand{\Naiara}{Silva, NT}
\newcommand{\Antonella}{Rella, A}
\newcommand{\Tyler}{Normile, T}
\newcommand{\Luna}{Joffe, LS}
\newcommand{\Patricia}{Tavares, PM}
\newcommand{\Glauber}{Araújo, GRS}
\newcommand{\Susana}{Frases, S}
\newcommand{\Erika}{Orner, EP}
\newcommand{\Amir}{Farnoud, AM}
\newcommand{\Bettina}{Fries, BC}
\newcommand{\Brian}{Sheridan, B}
\newcommand{\Leo}{Nimrichter, L}

% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% Icon fonts (requires using xelatex or luatex)
\usepackage[fixed]{fontawesome5}
\usepackage{academicons}

% Template variables for styling
\newcommand{\TablePad}{\vspace{-0.4cm}}
\newcommand{\SoftwareTitle}[1]{{\bfseries #1}}
\newcommand{\TableTitle}[1]{{\fontsize{12pt}{0}\selectfont \itshape #1}}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.04\textwidth} p{0.9\textwidth}@{}}
    \BODY
\end{tabularx}
}

% Macros to add links
\newcommand{\DOI}[1]{doi:\href{https://doi.org/#1}{#1}}
\newcommand{\GitHub}[1]{\newline • Code: \faGithub\ \href{https://github.com/#1}{#1}}


% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{10pt}{0}\selectfont #1--#2}
\newcommand{\Year}[1]{\fontsize{10pt}{0}\selectfont #1}
\newcommand{\now}{}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[left=0.5in,right=0.5in,top=0.7in,bottom=0.7in]{geometry}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.2}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{nosep}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts. Requires compilation with xelatex
%\usepackage{fontspec} % required to make older xelatex compile with UTF8

% Configure the font style for sections
\usepackage{sectsty}
\sectionfont{\vspace{0.1cm}\bfseries\fontsize{12pt}{0}\selectfont\uppercase}
\subsectionfont{\vspace{0.1cm}\mdseries\fontsize{12pt}{0}\selectfont\uppercase}

% Set the spacing for sections
%\usepackage{titlesec}
%\titlespacing{\section}{0pt}{0cm}{0.3cm}
%\titlespacing{\subsection}{0pt}{0.3cm}{0.3cm}

% Disable number of sections. Use this instead of "section*" so that the sections still
% appear as PDF bookmarks. Otherwise, would have to add the table of contents entries
% manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\chead{
    \itshape
    \fontsize{10pt}{12pt}\selectfont
    \MyName
    \hspace{0.2cm} -- \hspace{0.2cm}
    \Title
    \hspace{0.2cm} -- \hspace{0.2cm}
    \monthyear\today
}
\rhead{}
\cfoot{\fontsize{10pt}{0}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
    pdftitle={\MyName\ - \Title},
    pdfauthor={\MyName},
    linkcolor=blue,
    citecolor=blue,
    filecolor=black,
    urlcolor=MidnightBlue
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% No header for the first page
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% HEADER
{\fontsize{20pt}{0}\selectfont \MyName}	
\\%[0.1cm]
\rule{\textwidth}{0.2pt}
%\begin{minipage}[t]{0.195\textwidth}
%	 email: \href{mailto:\Email}{\Email}
%	 \\
%	 phone: {\phone}
    %website: \href{https://www.\Website}{\Website}
%\end{minipage}
%\begin{minipage}[t]{\textwidth}
  \begin{flushright}
    %\Affiliation
	%\\
	\Address, \City
	\\
	{\phone}
	\\
	\href{mailto:\Email}{\Email}
	\\
	ORCID: \href{https://orcid.org/\ORCID}{\ORCID}
	
	
  \end{flushright}
%\end{minipage}

I have a \textbf{PhD} in Biochemistry. During my \textbf{research career} I 
worked within different biology fields, from neuroscience and behaviour to fungi infection and 
extracellular vesicles. I also have experience working in 
\textbf{educational settings}, such as a museum and a botanical garden,
and a \textbf{charity}. I'm passionate about \textbf{science and education},
and I believe that through \textbf{mentoring} we can improve \textbf{equality
and diversity} in STEM. In the past year, I have been 
developing my \textbf{creative writing} skills which resulted in a
\textbf{children's book and a short story} in an anthology that will
be published this year. I want to combine art and science,
and make it \textbf{more accessible and engaging}. I also have been
working on \textbf{open projects} and developing my \textbf{coding skills}
through website development and data analysis.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Education}

\begin{EntriesTable}
    \Year{2018}  &
    \textbf{PhD in Biochemistry}, \textit{Federal University of Rio de Janeiro (UFRJ), Brazil.}
    \\
    \Year{2014}  &
    \textbf{MSc in Psychobiology}, \textit{University of São Paulo (USP), Brazil.}
    \\
    \Year{2011}  &
    \textbf{BSc and Teaching Degree in Biology}, \textit{State University of São Paulo (UNESP), Brazil.}
    \\
    
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Continuing Education}

\begin{EntriesTable}
	\Year{2022}  &
	\textbf{Write2 What's Next} -
	Online - \textit{Writing on the Wall, UK.}
	\\

	\Year{2021}  &
	\textbf{Write2Work} -
	Online - \textit{Writing on the Wall, UK.}
	\\

	\Year{2020}  &
	\textbf{Communication Skills for STEM Ambassadors} -
	Online - \textit{Future Learn, UK.}
	\\

	\Year{2019}  &
	\textbf{101 Web Development} -
	DevLeague - \textit{Honolulu, HI, USA.}
	\\

\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Career summary}

\begin{flushright} January 2022 - present 
\end{flushright}	
\textbf{Programme Intern at In2scienceUK} [Remote, UK].
\\
Contributing to the \textbf{development and delivery} of three programmes - the In2scienceUK summer programme, 
In2research and Alumni Community - for disadvantaged 
young people interested in pursuing a STEM career.
\\
\textit{Key responsibilities}
\\
\textbullet \ Creating communication material such as newsletters for volunteers 
\\
\textbullet \ Rebranding In2research webpage, updating content and structure
\\
\textbullet \ Participating, presenting, and assisting with online information sessions and workshops with volunteers, students, or external stakeholders
\\
\textbullet \ Budgeting for events
\\
\textbullet \ Supporting event planning, from defining objectives to debriefing afterwards
\\
\textbullet \ Updating and refining contact databases 
\\
\textbullet \ Drafting small grant proposals
\\
\textbullet \ Hosting internal and external team meetings, planning discussion points and meeting structure
\\
\textbullet \ Working with team communication and data organisation tools such as, Google Workspace, CRM, Work OS, and Wordpress
\\
\textit{Key achievements/projects}
\\
\textbullet \ Came up with a \textbf{strategic idea} of improving \textbf{volunteer engagement} through social media science interviews
\\
\textbullet \ Ongoing revision of our webpage for \textbf{better communication} with participants 
\\ 
\textbullet \ Applied IT and computer programming skills to make the \textbf{time consuming task} of scraping 
contacts from websites for volunteer recruitment \textbf{more efficient} by an order of magnitude
\\[0.1cm]

\begin{flushright} June 2019 - July 2019
\end{flushright}
\textbf{Education Assistant Intern at Lyon Arboretum} [USA].
\\
Working with \textbf{science and outreach} at an Arboretum that was part of University of Hawai’i.
\\
\textit{Key responsibilities}
\\
\textbullet \ Developing educational content and material for a field trip 
\\
\textbullet \ Communicating with different age groups/audiences through guided visits and outreach events
\\
\textbullet \ Assisting other departments with their conservation effort tasks such as replanting and trail maintenance
\\
\textbullet \ Presenting achievements to the team
\\
\textit{Key achievements/projects}
\\
\textbullet \ Created material about plant adaptations for a field trip for third graders \textbf{that is still used} by the organisation. It was \textbf{tailored for primary school pupils}, and based on the US National Curriculum. 
\\
\textbullet \ Received \textbf{positive feedback} and praise from coworkers for my final presentation
\\[0.1cm]

\begin{flushright} August 2017 - December 2018
\end{flushright}
\textbf{Research Support Specialist at Stony Brook University} [USA].
\\
\textbf{Designing, managing and developing} scientific projects with researchers at a University biomedical laboratory.
\\
\textit{Key responsibilities}
\\
\textbullet \ Managing different scientific projects from concept to delivery 
\\
\textbullet \ Communicating science efficiently through presentation and written scientific papers
\\
\textbullet \ Collecting, analysing, and interpreting results
\\
\textbullet \ Assisting peers and junior members with hands-on tasks and giving feedback on their projects 
\\
\textit{Key achievements/projects}
\\
\textbullet \ \textbf{Coordinated} groups of up to 14 scientists from up to six \textbf{different research groups} to \textbf{successfully complete and publish} two scientific papers. 
\\
\textbullet \ Established a \textbf{new field} of research in which new members of the laboratory have continue to developing
\\
\textbullet \ \textbf{Maintain my relationship} with the group to this day giving support to new members

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Other Experience}

\begin{EntriesTable}

\Year{now} &
\textbf{Demonstrator (Volunteer)} -
\textit{Aquarium of the World Museum, Liverpool, UK.}
\\

\Year{now}  &
\textbf{STEM Ambassador (Volunteer)} -
\textit{All about STEM, Liverpool, UK.}
\\
	
\Year{2020} & 
\textbf{Invited speaker (Volunteer)} -
\textit{Public School EMEF Prof. José Toledo de Mendonça, Brazil.}
\\

\Year{2009} &
\textbf{Organizing committee of the XIII Biology Week (Volunteer)} -
\textit{State University of São Paulo (UNESP), Brazil.}
\\


\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Technical Skills}

	\textbullet \ Bilingual (English and Portuguese)
	\textbullet \ Microsoft Office
	\textbullet \ Google Workspace and Google Drive
	\textbullet \ Work OS and CRM 
	\textbullet \ Website Development 
	\textbullet \ Basic Python and Jupyter Notebook
	\textbullet \ Basic JavaScript, HTML, CSS, and \LaTeX\
	\textbullet \ GitHub
	\textbullet \ Basic Image Editing and Vector Graphics Software
	\textbullet \ Data Processing and Statistical Analysis.


\end{document}
